State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2014-11-29 paper/chapters/2_data.tex
paper: update preprocessing

\section{Data}
Twitter is a social network and a microblogging service that
allows their users to compose and read so called 
\emph{tweets}. Each tweet 
is a text message and can contain up to 140 characters
including links, pictures\footnote{pictures are replaced 
by a url targeting a public available image resource}, and special tagged words.
These special words start with a well defined prefix 
and add semantic information to the prefixed word.
Table \ref{tab:twitterprefixes} shows an overview of 
common prefixes supported by Twitter and their purpose. 
The hashtag \# tags a special word, also known as hashtag. 
It is used to mark important keywords within the tweet.
There is also a at-sign-prefix \emph{@}, which allows 
to mention other Twitter users in a post. It's also possible to 
insert urls as part of the message. Regarding the hard message 
length limitation of a tweet, url-shortener are often used to
 insert longer urls.

@@

>>>>

\section{Data}
Twitter is a social network and a microblogging service that
allows their users to compose and read so called 
\emph{tweets}. The user registration it is not limited 
to professional writers, authors or similar expert groups 
and there are no quality safeguards or writing guidelines.

Each tweet is a text message and can contain up to 140 characters
including links, pictures\footnote{pictures are replaced 
by a url targeting a public available image resource}, and special tagged words.
These special tagged words start with a well defined prefix 
and add semantic information to the prefixed string.
Table \ref{tab:twitterprefixes} shows an overview of 
common prefixes supported by Twitter and their purpose. 
The hashtag \# labels a word, also known as hashtag. 
It is used to mark important keywords within tweets.
There is also a at-sign-prefix \emph{@}, which allows 
to mention and link other Twitter users in a post. Tweet composers can 
insert URLs as part of their messages. Regarding the hard 
length limitation of a tweet, url-shortener are often used to
insert longer internet addresses.

@@

The combination of the 140 character restriction and
the missing writing guidelines leads to another problem: 
Slang, emoticons and punctuation that are uncommon in longer 
text messages are heavily used.\autocite{davies2011}
In terms of sentiment analysis, tweet processing is more comparable to
sentence level analysis as paragraph analysis.

%These circumstances make it even harder to  ...

### 2014-11-29 paper/chapters/3_preprocessing.tex
paper: update preprocessing

\section{Preprocessing}
The Data-Preprocessing-Process is an essential part of sentiment-Analysis. Its goal is to prepare data
for the sentiment analysis and remove unnecessary parts.\autocite{Hemalatha2012}

Unnecessary Parts are:\autocite{Hemalatha2012}
\begin{enumerate}
    \item Remove URLs, Special Characters
    \item Filter Unnecesarry Words
    \item Remove Retweets
\end{enumerate}

Besondere an twitter: Hashtags, Mentions, Smileys
Tokenizen

>>>>

\section{Preprocessing}
The data preprocessing step is an essential 
part of sentiment analysis. Its goal is to prepare data
for the sentiment analysis and remove noisy, unnecessary, 
inconsistent or incomplete parts.\autocite{Hemalatha2012}
In a first step a tokenizer splits the tweet into conjugate parts, called words. 
The resulting list of words is filtered regarding the word class, 
the word itself and the intention of the sentiment analysis. 
In case of sentiment analysis of twitter posts it is common to 
remove the parts described in the following paragraphs.\autocite{Hemalatha2012}

\paragraph{URLs}
Uniform Resource Locators (URLs) refer to another site, which 
in fact can contain very important information, but the internet adress 
on its own is not of interest, because in the most cases it 
contains only auto-generated information, which can not be influenced 
by the poster.

\paragraph{Unnecesarry words}
It is not a ovious task to classify if a word is unnecesarry 
or not. But some word classes, like pronouns, articles or interrogatives
do not contain any relevant information and can be skipped. (TODO:Referenz)

\paragraph{Retweets}
Retweets reflect the postion of another person and are not always
created to express the same position (e.g. statement of sarcasm).

\paragraph{Repeated characters}
Tweets contain often deformed words 
containing repeated characters like `heeeey' or
`whuhuuu'. In this cases it is intended to reconstruct 
the correct english term and only if it is not 
possible or to sophisticated, the word is removed 
by the preprocessor.

\subsection{Tokenizer}
There are already several open source tokenizer implementations
available. Some popular programming libraries for the english 
language include the Stanford NLP PTBTokenizer
\footnote{http://nlp.stanford.edu/software/tokenizer.shtml} 
and the Apache OpenNLP Tokenizer\footnote{http://opennlp.apache.org/documentation/manual/opennlp.html}.
These examples are quite versatile and can be even 
used for different tasks and languages.
To overcome the special needs of sentiment analysis in terms of Twitter posts,
highly specialized Tokenizer were created (e.g. Carnegie 
Mellon Twokenizer\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}).
Some tokens like emoticons are difficult to handle. Although they 
are a good and popular ressource for sentiment analysis. \autocite{emoticons}
It is a sophisticated task to recognize them correctly and some Tokenizers 
like the Stanford NLP PTBTokenizer even skips them per default. 
The Carnegie Mellon's Twokenizer recognizes the related parts and
forwords them to the Tagger.

\subsection{Tagger}
